Modular Inverse Reinforcement Learning on Human Motion

### 2015-02-11 paper.tex
first version ok

\keywords{
Reinforcement learning, human cognition, inverse learning
}

@@

Figure~\ref{fig:avatar} shows the domain that we use in this paper. The pink
cylinders represent obstacles, that the player would be punished if running
into. The blue cylinders represent targets, that the player would be rewarded if
collected. There is also a grey path on the ground that the player can follow.
So, naturally, this domain has three subtasks, 1) following the path, 2)
collecting targets, 3) avoiding obstacles. This is an experiment used in the
literature to evaluate modular reinforcement learning
\cite{rothkopf2013modular}.

We will evaluate four different tasks. \bf{Task 1}, following the path only, and
ignoring other objects. \bf{Task 2}, following the path, while avoid the obstacles.
\bf{Task 3}, following the path, while attain targets when possible. \bf{Task 4},
following the path, collecting the targets and avoiding obstacles
simultaneously.
We conducted experiments to ask volunteers to accomplish different tasks and
recorded their trajectories. The human data are collected by the Center for
Perceptual Systems in University of Texas at Austin.

@@

We train the modules first to get $Q_i$ before running the inverse reinforcement
learing algorithm. For each module, the agent only considers the closest target
and the closest obstacle. For the path module, the path is defined as segments
of waypoints, so the closest waypoint is considered. The agent takes the
distance and angle to the closest objects as the state representation.

@@

\begin{figure}[h!]
\centering
\includegraphics[width=0.24\textwidth]{task_1.png}
\includegraphics[width=0.24\textwidth]{task_2.png}
\includegraphics[width=0.24\textwidth]{task_3.png}
\includegraphics[width=0.24\textwidth]{task_4.png}
\caption{The trajectories of humans and our agent in four different tasks. The
upper two are Task 1 and 2. The lower two are Task 3 and 4.}
\label{fig:exp}
\end{figure}

@@

We report the results in Figure~\ref{fig:exp}, same as Figure~\ref{fig:avatar},
the red circles are obstacles. The blue circles are targets. The gray line is
the path. The black lines are trajectories of human --- each line represents one
human trajectory.
Using the weights derived from the algorithm, the trajectories of our agents are
drawn in the green lines.

Although humans don't agree each other on how to avoid obstacles or collecting
targets, our agent can figure out what the humans are doing, and perform the
similar performance. Table~\ref{tb:human} and Table~\ref{tb:agent} show the
number of targets hit and number of obstacles hit. Note that the numbers bolded
are active modules in the corresponding task. We can observe that humans still
do better than our agent in these tasks.

\begin{figure}[h!]
\centering
\includegraphics[width=0.4\textwidth]{objValuesTask1.png}
\includegraphics[width=0.4\textwidth]{objValuesTask2.png}
\includegraphics[width=0.4\textwidth]{objValuesTask3.png}
\includegraphics[width=0.4\textwidth]{objValuesTask4.png}
\caption{Heatmaps of the $\log$ of values of Equation~\ref{eq:irl} for different
weights for the four tasks, respectively. The red zones indicate higher values.
From left to right are Task 1 to Task 4.}
\label{fig:heatmap}
\end{figure}

@@

Second, we also assumes independency between modules. Correlation between
modules doesn't impair our analysis in this paper. In Figure~\ref{fig:heatmap},
we can find that the target module and obstacle module tends to be negatively
correlated.

>>>>

\keywords{
Reinforcement learning, human motion, inverse learning
}

@@

Figure~\ref{fig:avatar} shows the domain that we use in this paper. The pink
cylinders represent obstacles, that the player would be punished if running
into. The blue cylinders represent targets, that the player would be rewarded if
collected. There is also a gray path on the ground that the player can follow.
So, naturally, this domain has three subtasks, 1) following the path, 2)
collecting targets, 3) avoiding obstacles. This is an experiment used in the
literature to evaluate modular reinforcement learning
\cite{rothkopf2013modular}.

We will evaluate four different tasks. {\bf Task 1}, following the path only, and
ignoring other objects. {\bf Task 2}, following the path, while avoid the obstacles.
{\bf Task 3}, following the path, while attain targets when possible. {\bf Task 4},
following the path, collecting the targets and avoiding obstacles
simultaneously.
We conducted experiments to ask volunteers to accomplish different tasks and
recorded their trajectories. The human data are collected by the Center for
Perceptual Systems in University of Texas at Austin.

@@

We train the modules first to get $Q_i$ before running the inverse reinforcement
learning algorithm. For each module, the agent only considers the closest target
and the closest obstacle. For the path module, the path is defined as segments
of waypoints, so the closest waypoint is considered. The agent takes the
distance and angle to the closest objects as the state representation.

@@

\begin{figure}[h!]
\centering
\includegraphics[width=0.24\textwidth]{task_1.png}
\includegraphics[width=0.24\textwidth]{task_2.png}
\includegraphics[width=0.24\textwidth]{task_3.png}
\includegraphics[width=0.24\textwidth]{task_4.png}
\caption{The trajectories of humans and our agent in four different tasks. From
left to right are Task 1 to Task 4. The active modules should be (Path),
(Obstacle + Path), (Target + Path), (Target + Obstacle + Path), respectively.}
\label{fig:exp}
\end{figure}

@@

We report the results in Figure~\ref{fig:exp}, same as Figure~\ref{fig:avatar},
the red circles are obstacles. The blue circles are targets. The gray lines are
the path. The black lines are trajectories of human --- each line represents one
human trajectory.
Using the weights derived from the algorithm, the trajectories of our agents are
drawn in green color.

Although humans don't agree each other on how to avoid obstacles or collecting
targets, our agent can figure out what the humans are doing, and perform a
similar trajectory. Table~\ref{tb:human} and Table~\ref{tb:agent} evaluate the
performance by showing the number of targets hit and number of obstacles hit.
Note that the numbers bold-ed are active modules in the corresponding task. We
can observe that humans still do better than our agent in these tasks.

\begin{figure}[h!]
\centering
\includegraphics[width=0.4\textwidth]{objValuesTask1.png}
\includegraphics[width=0.4\textwidth]{objValuesTask2.png}
\includegraphics[width=0.4\textwidth]{objValuesTask3.png}
\includegraphics[width=0.4\textwidth]{objValuesTask4.png}
\caption{Heatmaps of the $\log$ of values of Equation~\ref{eq:irl} for different
weights for the four tasks, respectively. The red zones indicate higher values.
The upper two are Task 1 and 2. The lower two are Task 3 and 4.
}
\label{fig:heatmap}
\end{figure}

@@

Second, we also assumes independency between modules. Correlation between
modules doesn't impair our analysis in this paper. In Figure~\ref{fig:heatmap},
we can tell that the target module and obstacle module tend to be negatively
correlated from the shape of the red zones.
